Type Evolution in Programming Systems

### 2024-05-28 paper.tex
orphaned text in extract entity

Many past improvements in the practice of programming worked by speeding up feedback loops,
both in collaboration with other programmers (through collaborative development tools
\cite{goldman2011real,kurniawan2015coder,replit}) and in individual's interaction with the
programming environment (through live programming \cite{rein2018exploratory}).

@@

@@

Acme Corp has a problem, for spreadsheets don't naturally support relationships between entities.
End-user databases like Airtable~\cite{airtable} and Notion~\cite{notion} support \textit{links}
between tables but do not provide operations that can do an \textit{Extract Entity}. Neither do
the established database products (see Related Work). Acme will need to write code or do a big manual conversion.

TODO: Maybe insert something about methodology in general?
(ref the table challenges paper? although this paper is no longer so much about challenges)

@@

\paragraph{Live programming.}
Live programming~\cite{tanimoto90, rein2018exploratory} seeks to speed up feedback in (mostly solo) programming.
% \cite{mcdirmid13, Rauch_2019, beckmann2021shortening}
% A special case of live programming is \emph{hot reloading} (also called \emph{hot swapping})~\cite{barenz2020essence, } that installs code changes into a running system preserving state but not attempting to migrate that state through type changes.
\citet{SemanticDeltas} proposes a research agenda for thoroughly live DSL programming focusing on \emph{Semantic Deltas} that unify edit-time and run-time change.
\citet{RuntimeConstraint} study the live modeling problem in Section \ref{livemodeling}. They use constraints supplied by the developer to solve for the best new runtime state following a DSL language evolution. \citet{vanRozen19} take an alternative approach to the same problem using \emph{origin tracking} in textual editing.
%\citet{vanRozen23} subsequently proposed a metaprogramming language for live DSL programming.

>>>>

Many past improvements in the practice of programming worked by speeding up feedback loops,
both in collaboration with other programmers (through collaborative development tools
\cite{ProGit, goldman2011real,kurniawan2015coder,replit}) and in individual's interaction with the
programming environment (through live programming \cite{rein2018exploratory}).

@@

\textcolor{red}{[JE. Found this snippet in the related work]
Acme Corp has a problem, for spreadsheets don't naturally support relationships between entities.
End-user databases like Airtable~\cite{airtable} and Notion~\cite{notion} support \textit{links}
between tables but do not provide operations that can do an \textit{Extract Entity}. Neither do
the established database products (see Related Work). Acme will need to write code or do a big manual conversion.
}

@@

\textcolor{red}{Maybe insert something about methodology in general?
(ref the table challenges paper? although this paper is no longer so much about challenges)}

@@

\paragraph{Live programming.}
Live programming~\cite{tanimoto90, rein2018exploratory} seeks to speed up feedback in (mostly solo) programming.
% \cite{mcdirmid13, Rauch_2019, beckmann2021shortening}
% A special case of live programming is \emph{hot reloading} or \emph{hot swapping})~\cite{barenz2020essence, hicks2005dynamic} that installs code changes into a running system preserving state but not attempting to migrate that state through type changes.
\citet{SemanticDeltas} proposes a research agenda for thoroughly live DSL programming focusing on \emph{Semantic Deltas} that unify edit-time and run-time change.
\citet{RuntimeConstraint} study the live modeling problem in Section \ref{livemodeling}. They use constraints supplied by the developer to solve for the best new runtime state following a DSL language evolution. \citet{vanRozen19} take an alternative approach to the same problem using \emph{origin tracking} in textual editing.
%\citet{vanRozen23} subsequently proposed a metaprogramming language for live DSL programming.
